Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-04-18 GWLDCI.tex
comments on positroid

Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}. These integrals are calculated via Wilson loops. The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}. With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}. Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.

@@

Finally, we describe several important types of matroids. A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$. A {\em positroid} is a matroid which can be realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$. Finally, a {\em uniform matroid} of rank $r$ is a matroid in which any set of size $\leq r$ is independent.

>>>>

Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}. These integrals are calculated via Wilson loops. The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of $\Gr(k,n)$ \cite{wilsonloop}. With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}. Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.

@@

Finally, we describe several important types of matroids. A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$. If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is a {\em positroid}.  In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.  In particular, the property of being a positroid is not preserved under matroid isomorphism.} that is realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$. Finally, a {\em uniform matroid} of rank $r$ is a matroid in which any set of size $\leq r$ is independent.
